Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-10-09 ms/main.tex
Add refernce to Fluctuations in spatial model figure in the text

\autoref{fig:spatial} shows that the highest cost of cooperation ($c$) that permits the evolution of cooperation in simulations of the spatial model roughly agrees with the conditions derived in Result 2.
Simulating a spatial model with local selection (i.e. sites can only be settled by offspring of neighbor parents) had only a minor affect, eliminating the stable coexistence.

@@

% Fluctuations in spatial model
\begin{figure}[h]
  \centering
   \includegraphics[scale=0.75]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
   \caption{
    \textbf{Coexistence of both phenotypes in spatial model.}
    The dyanmics of the frequancy of cooperators (green) and the frequency of defactors in the spatial model. 
    Both groups has the same initial frequency (0.5) and there are no fixation of one of the groups through the simulation.
    The frequency of cooperators oscillate around the initial frequency. Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$,
    horizontal transmission of cooperators $T_A = 0.4$, horizontal transmission of defactors $T_B = 0.435$ and cost $c=0.02$.
    }
    \label{fig:spatial_fluctuations}
  \end{figure}
  %TODO: edit this caption. DC

>>>>

\autoref{fig:spatial} shows that the highest cost of cooperation ($c$) that permits the evolution of cooperation in simulations of the spatial model roughly agrees with the conditions derived in Result 2.
An example for stable coexistence is shown in \autoref{fig:spatial_fluctuations}.
Simulating a spatial model with local selection (i.e. sites can only be settled by offspring of neighbor parents) had only a minor affect, eliminating the stable coexistence.

@@

% Fluctuations in spatial model
\begin{figure}[h]
  \centering
   \includegraphics[scale=0.75]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
   \caption{
    \textbf{Stable coexistence of both phenotypes in spatial model.}
    The dyanmics of the frequancy of cooperators (green) and the frequency of defactors in the spatial model. 
    Both groups has the same initial frequency (0.5) and there are no fixation of one of the groups through the simulation.
    The frequency of cooperators oscillate around the initial frequency. Here, population size is 10,000 (100-by-100 grid), selection operates globally, benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$,
    horizontal transmission of cooperators $T_A = 0.4$, horizontal transmission of defactors $T_B = 0.435$ and cost $c=0.02$.
    }
    \label{fig:spatial_fluctuations}
  \end{figure}
  %TODO: edit this caption. DC
